\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{xcolor}

\title{SE 3XA3: Problem Statement\\open-mastermind}

\author{204, Trident
		\\ Justin Rosner, rosnej1
		\\ Justin Prez, prezj
		\\ Harshil Modi, modih1
}

\date{}

%\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2020-01-22 & Justin Rosner, Justin Prez, Harshil Modi & Description of changes\\
\textcolor{red}{2020-03-21} & \textcolor{red}{Justin Rosner, Justin Prez, Harshil Modi} & \textcolor{red}{Changes made for Rev1}\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

As of 2017, the gaming industry is worth 18.4 billion and is forecasted to increase to 230 billion by 2022. Around the world millions of people are looking for the next trend in the gaming industry. As game developers with prior experience, we are working towards bringing back one of the most popular games of the 1970’s, ‘mastermind’. However, instead of just creating another copy of mastermind, we are developing a novel, user-friendly graphic user interface (GUI) and implementing additional levels of difficulty to challenge and captivate users. With this new design, our team aims to make mastermind a game that is commonly played on-the-go, and enjoyed by everyone.

Although mastermind is a simple game, complex logical thinking is correlated with playing the game properly. Historically this game has been used to test IQ levels in individuals. By reimplementing mastermind as a convenient, easy-to-use \sout{web} \textcolor{red}{mobile} application, we hope to promote the popularity of the game among the younger generation to instil innovative problem solving techniques. With more people gaining access to the internet everyday, we aim to provide a sense of assurance to parents that their children are learning something useful while playing a game they enjoy. \textcolor{red}{The stakeholders for Mastermind will thus be academics using the game to test for IQ levels, and kids in the age range of 9-14 looking for a new game to play.}

Our reimplementation of mastermind as a web application aims to make the game more accessible and user-friendly. Currently the game is playable from a computer terminal, which may pose as a challenge for some users to setup and play. However, almost all devices have access to a web browser, which the general population is a lot more comfortable and familiar using.

%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}
